---
title: "Data Analysis Project"
format: 
  html:
    toc: true
    css: "cisr_resources/css/styles.css"
    editor: visual
    embed-resources: true
---
 

::: {style="font-size: 200%;"}
## Introduction
:::

 

Shruti Chauhan,\
University of Galway, Ireland\
`s.chauhan4@universityofgalway.ie`

**Hobbies**

-   Love Sports

-   Sleeping

-   Grocery Shopping

 

## Data Handling

### Loading

Necessary Library for data loading is used. i.e. Dplyr.

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
echo = FALSE
```

```{r}
#Loading library
library(dplyr)

#CSV Files are loaded. 
setwd("dataset/")
data1 <- read.csv("Depression.csv")
data2 <- read.csv("Life expectancy.csv")
data3 <- read.csv("Suicide Rate.csv")
```

### Cleaning

Datasets are inspected for any missing values, and if any are found, they need to be replaced.

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data1))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))

```

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data2))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))
```

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data3))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))
```

### Merging

Datasets are merged on a common column and dataypes of the merged csv are displayed.

```{r}
# Merge the datasets on the common column
merged_data <- inner_join(data2, data3, by = "Country")

# Write the merged dataset to a new CSV file
write.csv(merged_data, "dataset/merged_data.csv", row.names = FALSE)

head(merged_data)
str(merged_data)

merged_data$GDP.per.capita <- as.numeric(gsub(",", "", merged_data$GDP.per.capita))

```

::: {.callout-important collapse="true"}
## Note

Depression CSV file is a textual data from a survey. Hence, not merged with the other two files.
:::

## Data Analysis

Quantitative and Qualitative analysis is performed on the datasets.

### Data Stream

As implied by its name, our presentation illustrates the progression of our datasets, depicting their interrelationships and informing about our ultimate analysis.

```{mermaid}
 flowchart LR
      A[Dataset 1] --> B["Men's Life Expectancy"]
    A --> |women| C["Women's Life Expectancy"]
    A --> D["Happiness Score"]
    A --> E["Fertility Rate"]
    A --> F[Country]
    
    G[Dataset 2] --> H["Suicide Rate"]
    G --> J["GDP per capita"]
    G --> L[Country]
    
    F --> L
    L -->|Data Merge|M[Modified Dataset]
    
    N[Dataset 3] --> O[Title]
    N--> P[Content]
    N --> Q[Score]
    M --> R[Suicide Prediction]
    P --> R
```

### Quantitative Analysis 1
A regression model is constructed to predict the suicide rate through inference.
```{r}
library(ggplot2)
library(plotly)

# Perform linear regression
model <- lm(Suicide.rate ~ Life.Expectancy..years....Men + Life.Expectancy..years....Women +
              Happiness.Score + Fertility.Rate..births.per.woman. + GDP.per.capita, data = merged_data)

# Summary of the regression model
summary(model)

# Create ggplot object
p <- ggplot(merged_data, aes(x = GDP.per.capita, y = Suicide.rate)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Linear Regression: Suicide Rate Prediction",
       x = "GDP per capita",
       y = "Suicide Rate") +
  theme_minimal()

# Convert ggplot object to Plotly
p_plotly <- ggplotly(p)

# Display the interactive plot
p_plotly
```

### Quantitative Analysis 2

```{r}
library(plotly)
library(dplyr)

# Scatter plot to examine the relationship between fertility rate and life expectancy
fertility_life_exp_scatter <- plot_ly(merged_data, x = ~Fertility.Rate..births.per.woman., y = ~Life.Expectancy..years....Women,
                                      mode = "markers", type = "scatter", color = ~Country,
                                      text = ~paste("Country: ", Country, "<br>Fertility Rate: ", Fertility.Rate..births.per.woman.,
                                                    "<br>Life Expectancy (Female): ", Life.Expectancy..years....Women)) %>%
  layout(title = "Fertility Rate vs. Life Expectancy (Female)",
         xaxis = list(title = "Fertility Rate"),
         yaxis = list(title = "Life Expectancy (Female)"))


# Display the plots
fertility_life_exp_scatter

```

### Qualitative Analysis

Qualitative analysis involves examining textual data, such as survey responses, to uncover themes and sentiments related to depression. Text mining techniques extract insights from the data, while word cloud visualizations highlight common words or themes. This helps understand the experiences and perspectives of individuals dealing with depression in the dataset.

```{r}
#STEP 1: Retrieving the data and uploading the packages

library(wordcloud)


library(RColorBrewer)


library(wordcloud2)


library(tm)

library(dplyr)

df <-read.csv("/Users/nareshkumar/MS5130-3/MS5130/dataset/Depression.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)

df <-head(df, n = 1000)


text <- df$title

docs <- Corpus(VectorSource(text))

#STEP 2: Clean the text data

docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))

#STEP 3: Create a document-term-matrix

dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 


words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)

#STEP 4: Generate the word cloud
set.seed(1234) # for reproducibility 
wordcloud(words = df$word, freq = df$freq, min.freq = 1,max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"), wordLengths=c(0,Inf))

```



