---
title: "Data Analysis Project"
format: 
  html:
    toc: true
    css: "cisr_resources/css/styles.css"
    editor: visual
    embed-resources: true
---

 

::: {style="font-size: 200%;"}
## Introduction
:::

 

Shruti Chauhan,\
University of Galway, Ireland\
`s.chauhan4@universityofgalway.ie`

**Hobbies**

-   Love Sports

-   Sleeping

-   Grocery Shopping

 

## Data Handling

### loading

Necessary Library for data loading is used. i.e. Dplyr.

```{r}
#Loading library
library(dplyr)

#CSV Files are loaded. 
setwd("dataset/")
data1 <- read.csv("Depression.csv")
data2 <- read.csv("Life expectancy.csv")
data3 <- read.csv("Suicide Rate.csv")
```

### Cleaning

Datasets are inspected for any missing values, and if any are found, they need to be replaced.

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data1))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))

```

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data2))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))
```

```{r}
# Calculate the number of missing values
missing_values <- sum(is.na(data3))

# Print the number of missing values
print(paste("Number of missing values in the dataset:", missing_values))
```

### Merging

Datasets are merged on a common column and dataypes of the merged csv are displayed.

```{r}
# Merge the datasets on the common column
merged_data <- inner_join(data2, data3, by = "Country")

# Write the merged dataset to a new CSV file
write.csv(merged_data, "dataset/merged_data.csv", row.names = FALSE)

head(merged_data)
str(merged_data)
```

::: {.callout-important collapse="true"}
## Note

Depression CSV file is a textual data from a survey. Hence, not merged with the other two files.
:::

## Data Analysis

Quantitative and Qualitative analysis is performed on the datasets. 

### Data Stream


```{mermaid}
 flowchart LR
      A[Dataset 1] --> B["Men's Life Expectancy"]
    A --> |women| C["Women's Life Expectancy"]
    A --> D["Happiness Score"]
    A --> E["Fertility Rate"]
    A --> F[Country]
    
    G[Dataset 2] --> H["Suicide Rate"]
    G --> J["GDP per capita"]
    G --> L[Country]
    
    F --> L
    L -->|Data Merge|M[Modified Dataset]
    
    N[Dataset 3] --> O[Title]
    N--> P[Content]
    N --> Q[Score]
    M --> R[Suicide Prediction]
    P --> R
```

